
% Template from Trey Hunner


%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.6in,top=0.4in,right=0.6in,bottom=0.2in]{geometry} % Document margins
\usepackage{lato}
\usepackage{color}
\newcommand\tab[1][0.80cm]{\hspace*{#1}}
\normalfont

\name{\Huge Andrew \ Tseng} % Your name
\address{andydomokun@gmail.com \ \ 832-520-0969  \  \ } % Your address

\begin{document}

%	EDUCATION SECTION
\begin{rSection}{\large Education}
{\bf University of Texas at Austin} \hfill {\bf Graduation Date: December 2018} \\
\/ Bachelor of Science in Computer Science, GPA: 3.2

\end{rSection}

%	WORK EXPERIENCE SECTION
\begin{rSection}{\large Work Experience}

\begin{rSubsection}{Kershner Trading Group - Software Engineer}{February 2019 - Present}{}{}
\item Improved the Locate Borrow application by removing C\# dependencies within the C++/CLR application. Added features in application UI to provide visual TCP socket statuses for DevOps staff.
\item Developed server to handle orders for new clients and translates FIX 4.2 messages to an internal message.
\item Developed test client to test fix server that takes in FIX 4.2 messages to pipeline in to order handling system.
\item Ported code from windows to Linux to fit new feed servers/hardware lead to improve latency in handling orders.
\item Built internal tools to monitor system of order management system and found 21 inter-application bugs.
\item Designed and developed backend feature of recycling shares within trader accounts for to use throughout trading day. 
\end{rSubsection}

\begin{rSubsection}{Vast.com - Software Engineer Intern}{Summer, 2017}{}{}
\item Worked with a team of 5 other interns in developing a side product for Vast.com
\item Utilized Vast.com's Carstory data to make a webpage to list out car 
    information for a used car pop-up.
\item Worked with other UX designers in designing posters/online ads to promote
    the car pop-up product.
\end{rSubsection}

\begin{rSubsection}{Compal Electronics - Software Engineer Intern}{Summer, 2016}{}{}
\item Rewrote developer admin database pages into templates and added management features.
\item Developed sanity tests to help with continuous integration to help find bugs in the in-house API.
\item Debugged and refactored MongoDB schema for new category of data in database. 
\item Researched IoT concepts/protocols for R\&D for potential uses on new products.
\end{rSubsection}

\begin{rSubsection}{University of Texas at Austin}{Spring 2016, 2017}{}{}
\item Led discussion sections that reviewed topics of the weekly lectures.
\item Helped grade weekly homework and developed homework and midterm/final problems.
\end{rSubsection}

\end{rSection}

% PROJECT SECTION
\begin{rSection}{\large Projects}
\begin{rSubsection}{Type Inference System in C}{{}}{}{}
     \item Implemented type inference features in C with the \textbf{auto} keyword.
     \item Created symbol table and file rewrite in replacing auto keyword to correct type.
     \item Rewrites the auto keyword to the type that it infers based on the C-program.
     \item Wrote test scripts in Bash to make find corner cases along with string parser that finds lexes within the input program.
\end{rSubsection}
\begin{rSubsection}{Linux Kernel}{}{}{}
     \item Developed Linux kernel in C++ featuring threads, concurrency tools, virtual memory, file systems and system calls. 
     \item Designed threading system in intention to prevent deadlocking and manage re-entrant functions.
     \item To avoid baggage that C++ brings, avoided using C++ STL throughout development.
\end{rSubsection}
\begin{rSubsection}{Lilypond - Facebook Messenger Bot}{}{}{}
     \item Facebook Messenger bot that converts textual music notes into a music sheet.
    \item Utilized ImageMagick, C++, NodeJS to convert and parse text and create
    music sheet PNG file. 
\end{rSubsection}
\end{rSection}

% SKILLS SECTION
\begin{rSection}{\large Languages and Tools}
    \textbf{Experience} : Python $\vert$ Java $\vert$ C/ C++ $\vert$ Visual Studio  $\vert$ *nix $\vert$ Git\\
    \textbf{Familiar} : MySQL $\vert$ R $\vert$ MATLAB $\vert$
    Verilog $\vert$  \LaTeX  $\vert$  Docker  $\vert$ Google Cloud Platform $\vert$ Javascript/React $\vert$ Jenkins $\vert$ Anaconda $\vert$ Microsoft SQL MS 
\end{rSection}      

% job description text block to game resume


\end{document}
\grid
